\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2019-03-08 presentations/cambridge-18-03-2019/presentation.tex
[Presentation] First commit, Cambridge '19 presentation

@@

\begin{frame}
  \centering
  \frametitle{Traditional stack pointers}
  \begin{tikzpicture}[scale=.45, every node={scale=.45}]
    % recurrent parts
    \begin{scope}
      \clip (-.1,-.1) rectangle (6.1,15.1);
      \fill[gray!20,draw=none,opacity=.8] (0,0) rectangle (6,15);
      \draw[draw=gray!80] (0,0) -- (0,15);
      \draw[draw=gray!80] (6,0) -- (6,15);
      \draw[fill=white] (0,-.5) rectangle (6,2.5) node[pos=.5] {\scriptsize lower stack frames...};
    \end{scope}
    \draw (-1.5,0) node {};
    \draw (-1.5,15) node {};
    % \draw[->] (-1,0) -- node[midway,sloped,above] {stack grows upward} (-1,15);

@@

\begin{frame}
  \frametitle{Naive stack and return capabilities}
  \centering
  \begin{tikzpicture}[scale=.45, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

@@

    % prepare call: store old return capability
    \draw<+-+(3)>[fill=gray!50] (0,6) rectangle node {\tiny old return cap code} (6,6.5);
    \begin{onlyenv}<+-+(2)>
      \draw[fill=gray!50] (0,5.5) rectangle node {\tiny old return cap data} (6,6);
      % \draw [decorate,decoration={brace,amplitude=10pt,raise=4pt},yshift=0pt]
      % (0,0) -- (0,16) node (oldframe1) [black,midway,xshift=-0.5cm] {};
      % \draw (0,5.75) edge[->,out=180,in=225] (oldframe1);
    \end{onlyenv}
    \begin{onlyenv}<+->
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt,aspect=.4},yshift=0pt]
      (6,2.5) -- (6,16) node (callerframe1) [draw=black,pos=.4,xshift=0.8cm] {};
      \draw node[fill=gray!50,right=0cm of callerframe1] (rp1l) {new return capability data};
      \draw ($(rp1l.west) + (-.1,.3)$) pic {lock};
    \end{onlyenv}
    \begin{onlyenv}<+->
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (6.5,6.5) -- (6.5,16) node[draw=black] (sp1) [black,midway,xshift=0.8cm] {};
      \draw node[right=0cm of sp1] (nsp) { new stack capability };
    \end{onlyenv}

@@

\begin{frame}
  \frametitle{Attack 1 on naive stack and return capabilities }
  \centering
  \begin{tikzpicture}[scale=.45, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

@@

\begin{frame}
  \frametitle{\stktokens{}}
  \begin{itemize}
  \item Check the base address of the stack capability before and after calls.
  \item Make sure that local stack frames are non-empty.
    % Not illustrated. Trusted code must claim spot on the call stack to make
    % sure that they are returned to.
  \item Create token and data return capability on call: split the stack
    capability in two to get a stack capability for your local stack frame and a
    stack capability for the unused part of the stack. The former is sealed and
    used for the data part of the return pair.
  \item Create code return capability on call: Seal the old program pointer.
  \item Reasonable use of seals: Return seals are only used to seal old program
    pointers, every return seal is only used for one call site, and they are not
    leaked. % If return seals are used for other things, like sealing arbitrary
            % code pointers, then they can be used as an unsealing mechanism.
            % If the same seal is used for multiple call sites, then we lose the
            % guarantee that we return to the correct place. One could use the
            % wrong return capability to return "out of order"
            % If return seals are leaked, then we have no guarantee about what
            % they are used for.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{\stktokens{} prevent attack 1}
  % Emphazise that it is dynamically enforced.
  % Other cases, see paper.
  \centering
  \begin{tikzpicture}[scale=.45, every node={scale=.5}]
    % recurrent parts
    \stdstackstart
    \draw (17.5,5.5) node {register file};
    \begin{scope}
      \clip (16.9,1.1) rectangle (18.1,5.1);
      \foreach \x in {1,2,...,4}
      {
        \draw[fill=white] (17,\x) rectangle (18,\x+1) node[pos=.5,color=mygreen] {};
      };
    \end{scope}
    \node (r1) at (17.75,4.5) {};
    \node (r2) at (17.75,3.6) {};

@@

\begin{frame}
  \frametitle{Attack 2 on naive stack and return capabilities }
  \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

    % first step: capabilities
    \begin{onlyenv}<+>
      \draw[fill=white] (0,2.5) rectangle (6,4) node[pos=.5] {\footnotesize current stack frame};
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
        (6.5,2.5) -- (6.5,16) node[draw=black] (sp1) [black,midway,xshift=0.8cm] {};
      \draw node[right=0cm of sp1] { stack pointer };
      % \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      % (6,0) -- (6,16) node (oldframe1) [black,midway,xshift=0.5cm] {};
      % \draw node[fill=gray!50,right=0cm of oldframe1] (rp1l) {return pointer data};
    \end{onlyenv}

    % attacker stores copy of stack pointer high in the stack
    \draw<+->[fill=gray!50] (0,2.5) rectangle (6,4) node[pos=.5] {\footnotesize caller stack frame};
    \begin{onlyenv}<.-.(2)>
      \actadv{(0,4)}{(6,7)}{callee stack frame}
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
        (6.5,4) -- (6.5,16) node[draw=black] (sp1) [black,midway,xshift=0.8cm] {};
      \draw node[right=0cm of sp1] { stack pointer };
    \end{onlyenv}
    \draw<+->[fill=white] (0,13) rectangle (6,13.5) node[pos=.5,color=myred] {\footnotesize copy of sp};
    \draw<.> (6,13.25) edge[myred,thick,->,in=45] (sp1);
    \begin{onlyenv}<+->
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
        (13.5,4) -- (13.5,16) node[draw=black] (spold) [black,midway,xshift=0.8cm] {};
      \draw (6,13.25) edge[myred,thick,->,in=45] (spold);
    \end{onlyenv}

    % attacker calls trusted code again
%    \draw<+->[fill=gray!50] (0,4) rectangle (6,7) node[pos=.5] {\footnotesize callee stack frame};
    \begin{onlyenv}<+->
      \inactadv{(0,4)}{(6,7)}{callee stack frame}
    \end{onlyenv}
    \begin{onlyenv}<.>
      \draw[fill=white] (0,7) rectangle (6,9) node[pos=.5] {\footnotesize callee (2) stack frame};
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
        (6.5,7) -- (6.5,16) node[draw=black] (sp1) [black,midway,xshift=0.8cm] {};
      \draw node[right=0cm of sp1] { stack pointer };
    \end{onlyenv}

    % attacker uses old stack pointer
    \draw<+->[fill=gray!50] (0,7) rectangle (6,9) node[pos=.5] {\footnotesize callee (2) stack frame};
    \begin{onlyenv}<.-.(1)>
      \actadv{(0,9)}{(6,12)}{callee (3) stack frame}
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (6.5,9) -- (6.5,16) node[draw=black] (sp1) [black,midway,xshift=0.8cm] {};
      \draw node[right=0cm of sp1] { stack pointer };
    \end{onlyenv}
    \draw<+> (spold) edge[->,color=myred,very thick,out=235,in=0] node[sloped, below] {read/write} (6,8);
  \end{tikzpicture}
\end{frame}

\begin{frame}
  \frametitle{\stktokens{} prevent attack 2}
  \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    % recurrent parts
    \stdstackstart

    \draw (16.5,5.5) node {register file};
    \begin{scope}
      \clip (15.9,1.1) rectangle (17.1,5.1);
      \foreach \x in {1,2,...,4}
      {
        \draw[fill=white] (16,\x) rectangle (17,\x+1) node[pos=.5,color=mygreen] {};
      };
    \end{scope}
    \node (r1) at (16.75,4.5) {};
    \node (r2) at (16.75,3.6) {};

    % Caller 
    \actsf{(0,2.5)}{(6,5)}{caller stack frame} 
    \begin{onlyenv}<+>
      \capbrace{(6.5,2.5)}{(6.5,16)}
      \draw node[right=0cm of sp1] { stack pointer };
      \draw (r1) edge[->,myred,thick,bend left,dashed] (sp1);
    \end{onlyenv}

    % Split the stack pointer
    \begin{onlyenv}<+>
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \capbrace[usp]{(6.5,5)}{(6.5,16)}
      \draw (r2) edge[->,myred,thick,bend left,dashed] (sp2);
      \draw (r1) edge[->,myred,thick,bend left, dashed] (usp);
      \draw node[right=0cm of usp] { stack pointer };
      \draw node[right=0cm of sp2] { private stack pointer };
    \end{onlyenv}

    % Callee called
    \begin{onlyenv}<+>
      \capbrace[usp]{(6.5,5)}{(6.5,16)}
      \draw (r1) edge[->,myred,bend left,dashed] (usp);
      \draw node[right=0cm of usp] { stack pointer };
      \inactsf{(0,2.5)}{(6,5)}{caller stack frame} 
      \actadv{(0,5)}{(6,8)}{callee stack frame}
    \end{onlyenv}

    \begin{onlyenv}<.->
      \capbrace[sp2]{(6.5,2.5)}{(6.5,5)}
      \draw node[fill=gray!50,right=0cm of sp2] { \phantom{return data pointer} };
      \draw (r2) edge[->,myred,bend left,dashed] (sp2);
      \draw node[right=0cm of sp2] { return data pointer };
    \end{onlyenv}

    \begin{onlyenv}<+>

      \capbrace[usp]{(13.5,5)}{(13.5,16)}
      \draw (6,13.25) edge[myred,thick,->,in=45,dashed] (usp);
      \draw node[right=0cm of usp] { stack pointer };

      \draw[fill=white] (0,13) rectangle (6,13.5) node[pos=.5,color=myred] {\footnotesize sp};
      \inactsf{(0,2.5)}{(6,5)}{caller stack frame} 
      \actadv{(0,5)}{(6,8)}{callee stack frame}
    \end{onlyenv}

    % At this point we have a linear point stored in a part of memory that it governs. In other words, no other capabilities can grant access to this part of memory, to the capabilitiy is essentially lost.
%    \draw<+> node[mygreen,cloud,cloud puffs=10.8,cloud puff arc=110, aspect=3, draw, fill=white, align=center] () at (4,10) { Stack pointer\\essentially lost.};

    \begin{onlyenv}<+->

      \capbrace[usp]{(13.5,5)}{(13.5,16)}
      \draw (6,13.25) edge[myred,thick,->,in=45,dashed] (usp);
      \draw node[right=0cm of usp] { stack pointer };

      \begin{scope}
        \fill[fill=gray!50] (0,2.5) rectangle (6,15) node[pos=.5,color=black] {};
        \draw (0,0) -- (0,15);
        \draw (6,0) -- (6,15);
      \end{scope}
      \draw[fill=gray!50] (0,13) rectangle (6,13.5) node[pos=.5,color=myred,dashed] {\footnotesize sp};
      \inactsf{(0,2.5)}{(6,5)}{caller stack frame} 
      \inactadv{(0,5)}{(6,8)}{callee stack frame}
      \actsf{(0,8)}{(6,10.5)}{callee (2) stack frame} 
  \end{onlyenv}

  \draw<+>[mygreen,very thick] (-0.5,7.5) -- (6.5,11);
  \draw<.>[mygreen,very thick] (-0.5,11) -- (6.5,7.5);
  \draw<.> node[mygreen,cloud,cloud puffs=10.8,cloud puff arc=110, aspect=3, draw, fill=white, align=center] () at (14,7) { No stack pointer\\for callee (2)!};

  \end{tikzpicture}
\end{frame}

\begin{frame}
  \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    \frametitle{Attack 3 on naive stack and return capabilities}
    \begin{scope}
    \clip (-.1,-.1) rectangle (5.1,10.1);
    \fill[fill=gray!50] (0,0) rectangle (5,10);
    \draw (0,0) -- (0,10);
    \draw (5,0) -- (5,10);
    \end{scope}
    \draw (2.5,11) node {code memory};

    \begin{scope}
    \clip (12.9,3.9) rectangle (18.1,11.1);
    \fill[fill=gray!50] (13,4) rectangle (18,11);
    \draw (13,4) -- (13,11);
    \draw (18,4) -- (18,11);
    \end{scope}
    \draw (15.5,12) node {more code memory};

    \begin{scope}
    \clip (12.9,-.1) rectangle (18.1,2.1);
    \fill[fill=gray!50] (13,0) rectangle (18,2);
    \draw (13,0) -- (13,2);
    \draw (18,0) -- (18,2);
    \end{scope}
    \draw (14.5,3) node {heap memory};

\note{Caller calls callee}
    \draw<+->[fill=white] (0,1) rectangle (5,4) node[pos=.5] {\footnotesize caller code};

    \begin{onlyenv}<+->
      \capbrace[ret1]{(5.1,1)}{(5.1,4)}
      \draw node[fill=gray!50, right=0cm of ret1] { \phantom{ret-ptr} };
      \draw node[right=0cm of ret1] { ret-ptr };
    \end{onlyenv}

\note{Callee has access to some place to store things.}
    \begin{onlyenv}<+->
      \draw[fill=gray!30] (0,1) rectangle (5,4) node[pos=.5] {\footnotesize caller code};
      \draw[fill=white] (13,5) rectangle (18,6) node[pos=.5] {\footnotesize callee code};
      \draw[fill=white] (13,1) rectangle (18,1.5) node[pos=.5] {};
    \end{onlyenv}

    \begin{onlyenv}<.-.(2)>
      \draw [decorate,decoration={brace,amplitude=2pt,mirror,raise=4pt},yshift=0pt]
      (18.1,1) -- (18.1,1.5) node[draw=black] (copy) [black,midway,xshift=0.5cm] {};
      \draw (18,5.5)  edge[->,bend left] (copy);
    \end{onlyenv}

\note{Callee stores the return pointer they got from caller.}
    \begin{onlyenv}<+->
      \draw[fill=white] (13,1) rectangle (18,1.5) node[pos=.5] {\scriptsize {\color{myred} copy of ret-ptr}};
      \draw (13,1.25) edge[->,myred,thick,bend left] (ret1);
    \end{onlyenv}

\note{Callee calls callee (1)}
    \begin{onlyenv}<+->
      \draw [decorate,decoration={brace,amplitude=3pt,raise=4pt},yshift=0pt]
      (12.9,5) -- (12.9,6) node[draw=black] (ret2) [black,midway,xshift=-0.8cm] {};
      \draw node[fill=gray!50,left=0cm of ret2] { \phantom{ret-ptr (1)} };
      \draw node[left=0cm of ret2] (retptr1) { ret-ptr (1) };
    \end{onlyenv}

    \begin{onlyenv}<+->
      \draw[fill=white] (0,5) rectangle (5,8) node[pos=.5] {\footnotesize callee code (1)};
      \draw[fill=gray!30] (13,5) rectangle (18,6) node[pos=.5] {\footnotesize callee code};
      \draw[fill=gray!30] (13,1) rectangle (18,1.5) node[pos=.5] {\scriptsize {\color{myred} copy of ret-ptr}};
    \end{onlyenv}

\note{Callee (1) calls callee (2)}
    \begin{onlyenv}<+->
      \capbrace[ret3]{(5.1,5)}{(5.1,8)}
      \draw node[fill=gray!50,right=0cm of ret3] { \phantom{ret-ptr (2)} };
      \draw node[right=0cm of ret3] (retptr2) { ret-ptr (2) };
    \end{onlyenv}

    \begin{onlyenv}<+->
      \draw[fill=gray!30] (0,5) rectangle (5,8) node[pos=.5] {\footnotesize callee code (1)};
      \draw[fill=white] (13,7) rectangle (18,10) node[pos=.5] {\footnotesize callee code (2)};
    \end{onlyenv}
\note{Callee (2) colludes with callee}
    \begin{onlyenv}<+->
      \draw (21,7.5) node[devil,opaque=0.5,mirrored,minimum size=1cm] {};
    \end{onlyenv}
\note{Callee (2) has access to ret-ptr (the return pointer caller passed to callee)}
    \begin{onlyenv}<+->
      \draw [decorate,decoration={brace,amplitude=2pt,mirror,raise=4pt},yshift=0pt]
      (18.1,1) -- (18.1,1.5) node[draw=black] (copy) [black,midway,xshift=0.5cm] {};
      \draw (18,8.25)  edge[->,myred,thick,bend left] (copy);
      \draw[fill=white] (13,1) rectangle (18,1.5) node[pos=.5] {\scriptsize {\color{myred} copy of ret-ptr}};
    \end{onlyenv}

\note{Callee (2) uses ret-ptr to return}
    \begin{onlyenv}<+->
      \draw[fill=gray!30] (13,7) rectangle (18,10) node[pos=.5] {\footnotesize callee code (2)};
      \draw[fill=white] (0,1) rectangle (5,4) node[pos=.5] {\footnotesize caller code};
      \draw[fill=gray!30] (13,1) rectangle (18,1.5) node[pos=.5] {\scriptsize {\color{myred} copy of ret-ptr}};
    \end{onlyenv}

    \note{This breaks well-bracketedness as ret-ptr (2) and ret-ptr (1) was not returned to}
    \begin{onlyenv}<+->
      \draw node [ellipse, fit=(retptr1) (retptr2), draw, myred] { };
      \draw node[myred,cloud,cloud puffs=10.8,cloud puff arc=110, aspect=3, draw, fill=white, align=center] () at (12,10) { These were skipped!};  
    \end{onlyenv}
  \end{tikzpicture}
\end{frame}

>>>>

\tikzset{capa/.style={decoration={markings,mark=at position 0 with %
      {\fill[black] circle(1.5pt);}}}}

@@

\begin{frame}
  \centering
  \frametitle{Traditional stack pointers}
  \begin{tikzpicture}[scale=.45, every node={scale=.45}]
    % recurrent parts
    \begin{scope}
      \clip (-.1,-.1) rectangle (6.1,15.1);
      \fill[gray!20,draw=none,opacity=.8] (0,0) rectangle (6,15);
      \draw[draw=gray!80] (0,0) -- (0,15);
      \draw[draw=gray!80] (6,0) -- (6,15);
      \draw[fill=white] (0,-.5) rectangle (6,2.5) node[pos=.5] {\scriptsize lower stack frames...};
    \end{scope}
    \draw (-1.5,0) node {};
    \draw (-1.5,15) node {};
    % \draw[->] (-1,0) -- node[midway,sloped,above] {stack grows upward} (-1,15);
    \draw (20,14) node {\phantom{heap memory}};

@@

\begin{frame}
  \frametitle{Naive stack and return capabilities}
  \centering
  \begin{tikzpicture}[scale=.45, every node={scale=.5}]
    % recurrent parts
    \stdstackstart
    \draw (20,14) node {\phantom{heap memory}};
    \regfile

@@

    % prepare call: store old return capability
    \begin{onlyenv}<+-+(3)>
      \draw[fill=gray!50] (0,5.5) rectangle node {\tiny old return cap data} (6,6);
      % \draw [decorate,decoration={brace,amplitude=10pt,raise=4pt},yshift=0pt]
      % (0,0) -- (0,16) node (oldframe1) [black,midway,xshift=-0.5cm] {};
      % \draw (0,5.75) edge[->,out=180,in=225] (oldframe1);
    \end{onlyenv}
    \draw<+-+(2)>[fill=gray!50] (0,6) rectangle node {\tiny old return cap code} (6,6.5);
    \begin{onlyenv}<+->
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt,aspect=.4},yshift=0pt]
      (6,2.5) -- (6,16) node (callerframe1) [draw=black,pos=.4,xshift=0.8cm] {};
      \draw node[fill=gray!50,right=0cm of callerframe1] (rp1l) {new return capability data};
      \draw ($(rp1l.west) + (-.1,.3)$) pic {lock};
    \end{onlyenv}
    \begin{onlyenv}<+->
      \draw [decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt]
      (6.5,6.5) -- (6.5,16) node[draw=black] (sp1) [black,midway,xshift=0.8cm] {};
      \draw node[right=0cm of sp1] (nsp) { new stack capability };
    \end{onlyenv}

@@

\begin{frame}
  \frametitle{Attack on naive stack and return capabilities }
  \centering
  \begin{tikzpicture}[scale=.45, every node={scale=.5}]
    % recurrent parts
    \stdstackstart
    \draw (20,14) node {\phantom{heap memory}};
    \regfile

@@

\begin{frame}
  \frametitle{Linear capabilities}
  \begin{columns}
    \begin{column}{.6\textwidth}
      \begin{tikzpicture}[scale=.45, every node={scale=.5}]
        \scope
          \clip (-.1,-.1) rectangle (6.1,14.9);
          \fill[draw,fill=white] (0,0) rectangle (6,15);
        \endscope
        % \draw[->] (-2,0) -- node[midway,sloped,above] {stack grows upward}
        % (-2,15);
        \foreach \X in {0,0.5,...,14} {
          \fill[draw,fill=white] (0,\X) rectangle (6,\X+.5) node[pos=.5] { };
        };
        \draw (-0.5,0.25) node[align=right] { \scriptsize 0 };
        \draw (-0.5,4.25) node[align=right] { \scriptsize 8 };
        \draw (-0.5,8.25) node[align=right] { \scriptsize 16 };
        \draw (-0.5,12.25) node[align=right] { \scriptsize 24 };

  \begin{scope}
    \clip (11.9,2.6) rectangle (13.6,11.6);
    \foreach \X in {0,1.5,...,7.5} {
      \fill[draw,fill=white] (12,10 - \X) rectangle (13.5,11.5-\X) node[pos=.5] { };
    };
  \end{scope}
  \draw (12.75,12.25) node[align=center] {Register File};
  \draw (6.5,14.325) node[anchor=west, align=left] {Memory}; \draw[->] (-1.5,0) -- (-1.5,4.5);

  % Mem data
  \draw<1-> (3,0.75) node { \scriptsize 42 };
  \draw<1-> (3,1.25) node { \scriptsize 2 };
  \draw<1-> (3,1.75) node { \scriptsize 14 };
  \draw<1-> (3,2.75) node { \scriptsize 10 };
  \draw<1-> (3,2.25) node { \scriptsize 19 };
  \draw<1-> (3,3.75) node { \scriptsize 0 };
  \draw<1-> (3,3.25) node { \scriptsize 0 };
  \draw<1-> (3,4.25) node { \scriptsize 0 };
  \draw<1-> (3,4.75) node { \scriptsize 0 };
  \draw<1-> (3,5.75) node { \scriptsize 3 };
  \draw<1-> (3,6.25) node { \scriptsize 20 };
  \draw<1-> (3,6.75) node { \scriptsize 21 };
  \draw<1-> (3,7.25) node { \scriptsize 11 };
  \draw<1-> (3,7.75) node { \scriptsize 10 };
  \draw<1-> (3,8.25) node { \scriptsize 15 };
  \draw<1-> (3,8.75) node { \scriptsize 19 };
  \draw<1-> (3,9.25) node { \scriptsize 29 };
  \draw<1-> (3,9.75) node { \scriptsize 0 };
  \draw<1-> (3,10.25) node { \scriptsize 0 };
  \draw<1-> (3,10.75) node { \scriptsize 0 };
  \draw<1-> (3,11.25) node { \scriptsize 0 };
  \draw<1-> (3,11.75) node { \scriptsize 0 };
  \draw<1-> (3,12.75) node { \scriptsize 0 };
  \draw<1-> (3,13.25) node { \scriptsize 0 };
  \draw<1-> (3,13.75) node { \scriptsize 64 };
  \draw<1-> (3,14.25) node { \scriptsize 5 };
  % Reg data
  \draw<1-> (12.75,10.75) node { \scriptsize 8 };
  \draw<1-> (12.75,7.75) node { \scriptsize 24 };
  \draw<1-> (12.75,6.25) node { \scriptsize 16 };
  \draw<1-> (12.75,4.75) node { \scriptsize 2 };

  % Mem pointers
  \draw<1> (3,12.25) node { \scriptsize 16 };
  \draw<1> (3,5.25) node { \scriptsize 9 };
  \draw<1> (3,0.25) node { \scriptsize 8 };
  % Reg pointers
  \draw<1> (12.75,9.25) node { \scriptsize 0 };

  % Mem pointers HL
  \draw<2> (3,12.25) node { \color{red} \scriptsize 16 };
  \draw<2> (3,5.25) node { \color{red} \scriptsize 11 };
  \draw<2> (3,0.25) node { \color{red} \scriptsize 8 };
  % Reg pointers HL
  \draw<2> (12.75,9.25) node { \color{red} \scriptsize 0 };

  \draw<3> (12.75,9.25) node { };

  % Mem capabilities
  \draw<4->[capa] (3,12.25) edge[postaction={decorate}] (6.1,12.25 );
  \draw<4> (6.1,12.25) edge[-latex,in=0,out=0] (6.1,8.25);
  \draw<4->[capa] (3,5.25) edge[postaction={decorate}] (6.1,5.25);
  \draw<4> (6.1,5.25) edge[-latex,in=0,out=0] (6.1,6.75);
  \draw<4->[capa] (3,0.25) edge[postaction={decorate}] (6.1,0.25);
  \draw<4> (6.1,0.25) edge[-latex,in=0,out=0] (6.1,4.25);

  % Reg pointers HL
  \draw<4->[capa] (12.75,9.25) edge[postaction={decorate}] (12.0,9.25);
  \draw<4> (12.0,9.25) edge[-latex,in=0,out=180] (6.1,0.25);

  % Mem capabilities \w auth
  \draw<5> (6.1,12.25) edge[-latex,in=0,out=0] (6.5,8.25);
  \draw<5->[decorate,decoration={brace,amplitude=2pt,raise=0pt,aspect=0.55,mirror},yshift=0pt] (6.3,5.5) -- (6.3,10.5) node (e) [black,midway,xshift=0.8cm] {};

  \draw<5> (6.1,5.25) edge[-latex,in=0,out=0] (6.3,6.75);
  \draw<5-> [decorate,decoration={brace,amplitude=2pt,raise=0pt,aspect=0.5,mirror},yshift=0pt] (6.1,6) -- (6.1,7.5) node (e) [black,midway,xshift=0.8cm] {};

  \draw<5> (6.1,0.25) edge[-latex,in=0,out=0] (6.5,4.25);
  \draw<5-> [decorate,decoration={brace,amplitude=2pt,raise=0pt,aspect=0.5,mirror},yshift=0pt] (6.3,3) -- (6.3,5.5) node (e) [black,midway,xshift=0.8cm] {};

  % Reg pointers HL \w auth
  \draw<5> (12.0,9.25) edge[-latex,in=0,out=180] (6.3,0.355);
  \draw<5-> [decorate,decoration={brace,amplitude=2pt,raise=0pt,aspect=0.1,mirror},yshift=0pt] (6.1,0) -- (6.1,3.5) node (e) [black,midway,xshift=0.8cm] {};

  % Mem capabilities \w auth & perm
  \draw<6-> (6.1,12.25) edge[-latex,in=0,out=0] node[right] {\scriptsize \textsc{r}} (6.5,8.25);

  \draw<6-> (6.1,5.25) edge[-latex,in=0,out=0] node[right] {\scriptsize \textsc{rw}} (6.3,6.75);

  \draw<6-> (6.1,0.25) edge[-latex,in=0,out=0] node[right] {\scriptsize \textsc{r}} (6.5,4.25);

  % Reg pointers HL \w auth & perm
  \draw<6-> (12.0,9.25) edge[-latex,in=0,out=180] node[right] {\scriptsize \textsc{rx}} (6.3,0.355);
\end{tikzpicture}
\end{column}
\begin{column}{0.4\textwidth}
  \onslide<3->{Replace pointers with capabilities}
  \begin{itemize}
  \item<4-> Pointer
  \item<5-> Range of authority
  \item<6-> Permission
  \end{itemize}
  \onslide<7->{Dynamically enforced}
  \begin{itemize}
  \item<8-> Cap. aware instructions
  \item<9-> Tagged memory
  \end{itemize}
\end{column}
\end{columns}
\end{frame}

\begin{frame}
  \frametitle{\stktokens{} prevents the attack}
  % Emphazise that it is dynamically enforced.
  % Other cases, see paper.
  \centering
  \begin{tikzpicture}[scale=.45, every node={scale=.5}]
    % recurrent parts
    \stdstackstart
    \draw (20,14) node {\phantom{heap memory}};

    \regfile

@@

% \begin{frame}
%   \frametitle{\stktokens{} enforces single stack}
%   \begin{tikzpicture}[scale=.5, every node={scale=.5}]
%     % recurrent parts
%   \scope
%     \clip (-.1,-.1) rectangle (6.1,15.1);
%     \fill[fill=white] (0,0) rectangle (6,15);
%     \draw (0,0) -- (0,15);
%     \draw (6,0) -- (6,15);
%     \draw[fill=gray!50] (0,-.5) rectangle (6,1.5) node[pos=.5,color=black] {\footnotesize higher stack frames...};
%   \endscope
%   % \draw[->] (-2,0) -- node[midway,sloped,above] {stack grows upward} (-2,15);

%   \begin{scope}
%     \fill[gray!50] (13,0) rectangle (18,13);
%     \draw (13,0) -- (13,13);
%     \draw (18,0) -- (18,13);
%     \draw (15.5,14) node {heap};
%   \end{scope}

% \note{Caller calls callee (split stack pointer to make ret-ptr-d)}
%   \begin{onlyenv}<+>
%     \actsf{(0,1.5)}{(6,4.5)}{caller stack frame}
%   \end{onlyenv}
%   \begin{onlyenv}<.>
%     \capbrace[sp]{(6.1,1.5)}{(6.1,15)}
%     \draw node[right=0cm of sp] { sp };
%   \end{onlyenv}

%   \begin{onlyenv}<+->
%     \inactsf{(0,1.5)}{(6,4.5)}{caller stack frame}
%   \end{onlyenv}
%   \begin{onlyenv}<.>
%     \actadv{(0,4.5)}{(6,7.5)}{callee stack frame}
%     \draw[fill=white] (13,6) rectangle (18,9) node[pos=.5] {\footnotesize adv mem};
%   \end{onlyenv}
%   \begin{onlyenv}<.>
%     \capbrace[sp2]{(6.1,4.5)}{(6.1,15)}
%     \capbrace[sp]{(6.1,1.5)}{(6.1,4.5)}
%     \draw node[right=0cm of sp2] { sp2 };
%     \draw node[right=0cm of sp, fill=gray!50] { ret-ptr-d };
%     \draw (13,6.5) edge[myred,bend right,thick,->,dashed] (sp);
%   \end{onlyenv}

%   \begin{onlyenv}<+>
%     \capbrace[sp3]{(6.1,9.5)}{(6.1,15)}
%     \capbrace[sp2]{(6.1,4.5)}{(6.1,9.5)}
%     \capbrace[sp]{(6.1,1.5)}{(6.1,4.5)}
%     \draw node[right=0cm of sp3] { sp3 };
%     \draw node[right=0cm of sp2] { sp2 };
%     \draw node[right=0cm of sp, fill=gray!50] { ret-ptr-d };
%     \draw (13,7.5) edge[myred,bend right,thick,->,dashed] (sp2);
%     \draw (13,6.5) edge[myred,bend right,thick,->,dashed] (sp);
%   \end{onlyenv}
%   \begin{onlyenv}<.->
%     \actsf{(0,9.5)}{(6,11.5)}{callee stack frame (1)}
%   \end{onlyenv}
%   \begin{onlyenv}<.>
%     \inactadv{(0,4.5)}{(6,7.5)}{callee stack frame}
%     \draw[fill=gray!30] (13,6) rectangle (18,9) node[pos=.5] {\footnotesize adv mem};
%   \end{onlyenv}

%   \begin{onlyenv}<+>
%     \capbrace[sp4]{(6.1,11.5)}{(6.1,15)}
%     \capbrace[sp3]{(6.1,9.5)}{(6.1,11.5)}
%     \capbrace[sp2]{(6.1,4.5)}{(6.1,9.5)}
%     \capbrace[sp]{(6.1,1.5)}{(6.1,4.5)}
%     \draw node[right=0cm of sp4] { sp4 };
%     \draw node[right=0cm of sp3, fill=gray!50] { sp3 };
%     \draw node[right=0cm of sp2] { sp2 };
%     \draw node[right=0cm of sp, fill=gray!50] { ret-ptr-d };
%     \draw (13,8.5) edge[myred,bend right,thick,->,dashed] (sp3);
%     \draw (13,7.5) edge[myred,bend right,thick,->,dashed] (sp2);
%     \draw (13,6.5) edge[myred,bend right,thick,->,dashed] (sp);
%   \end{onlyenv}
%   \begin{onlyenv}<.->
%     \inactsf{(0,9.5)}{(6,11.5)}{callee stack frame (1)}
%     \actadv{(0,11.5)}{(6,14.5)}{callee stack frame (2)}
%   \end{onlyenv}
%   \begin{onlyenv}<.>
%     \actadv{(0,4.5)}{(6,7.5)}{callee stack frame}
%     \draw[fill=white] (13,6) rectangle (18,9) node[pos=.5] {\footnotesize adv mem};
%   \end{onlyenv}

%   \begin{onlyenv}<+->
%     \capbrace[sp4]{(6.1,11.5)}{(6.1,15)}
%     \capbrace[sp3]{(6.1,9.5)}{(6.1,11.5)}
%     \capbrace[sp]{(6.1,1.5)}{(6.1,9.5)}
%     \draw node[right=0cm of sp4, fill=gray!50] { sp4 };
%     \draw node[right=0cm of sp3, fill=gray!50] { sp3 };
%     \draw node[right=0cm of sp] { sp };
%     \draw (13,8.5) edge[myred,bend right,thick,->,dashed] (sp3);
%   \end{onlyenv}
%   \begin{onlyenv}<.->
%     \inactsf{(0,9.5)}{(6,11.5)}{callee stack frame (1)}
%     \inactadv{(0,11.5)}{(6,14.5)}{callee stack frame (2)}
%     \actsf{(0,1.5)}{(6,4.5)}{caller stack frame}
%     \draw[fill=white] (13,6) rectangle (18,9) node[pos=.5] {\footnotesize adv mem};
%   \end{onlyenv}
%   \begin{onlyenv}<+->
%     \draw[mygreen,very thick] (2.5,10) -- (3.5,9);
%     \draw[mygreen,very thick] (3.5,10) -- (2.5,9);
%     \draw node[mygreen,cloud,cloud puffs=10.8,cloud puff arc=110, aspect=3, draw, fill=white, align=center, anchor=west] () at (4,9.5) { Base check fails!};  
%   \end{onlyenv}
% \end{tikzpicture}
% \end{frame}
